Supplementary Material

### 2022-06-24 text/Draft.tex

@@

Once we suppress the initial radiation that is shed by the seed soliton during the relaxation process, the isolated soliton propagates generating a narrow-spectrum Cherenkov radiation. As an example we can consider Fig.~\ref{fig:Fig1}. Panel Fig.~\ref{fig:Fig1}b shows a normalized spectral density at the output of the simulation. There one can notice that on top of the input spectrum (plotted by thin black line) arise two additional spectral lines in the output spectrum (plotted by thicker gray line). Panel Fig.~\ref{fig:Fig2}c demonstrates resonance conditions~\eqref{eq:CherenkovRadiationResonanceCondition} and~\eqref{eq:FWMRadiationResonanceCondition}: black curve corresponds to the left-hand's side of both equations $\beta(\omega)$, horizontal lines correspond to the right-hand's sides. Intersections between the dispersive curve and the horizontal lines that contribute to Cherenkov radiation are marked separately: \circled{1}~is the radiation due to the second component of the soliton as predicted by equation~\eqref{eq:CherenkovRadiationResonanceCondition}, \circled{2}~is due to beat between the components with wavenumber $2 k_{2} - k_{1}$ as predicted by~\eqref{eq:FWMRadiationResonanceCondition}.

% A symmetric situation (resonances due to the second component and to beat with wavenumber $2 k_{1} - k_{2}$) turns out difficult to observe for the reasons yet unknown.

\begin{figure}[t]
  \includegraphics{{Figures/Fig1}.pdf}
  \caption{(color online) Cherenkov radiation of an isolated soliton produced by the soliton with $\omega_{1} = 1.010$~rad/fs. (a) time-domain view (b) input and output spectra (c) resonance conditions diagram.}%
  \label{fig:Fig1}
\end{figure}

@@

The first configuration we consider is very close to the degenerate case where the wavenumbers of the individual soliton components $k_{1}$ and $k_{2}$ coincide. Equation~\eqref{eq:Type1ResonanceCondition} then turns into equation~\eqref{eq:Type0ResonanceCondition}. This case resembles the case of fundamental single-component solitons~\cite{yulin2004four}. However, due to shape of the dispersive curve $\beta(\omega)$ there is now more than one nontrivial solution to equation~\eqref{eq:Type0ResonanceCondition} and a single incident frequency corresponds up to four possible resonances. This configuration can be seen in Fig.~\ref{fig:Fig1}. In practice, only some of them actually contribute to the scattered radiation. Again, those solution are separately marked on a diagram on panel~\ref{fig:Fig1}c: \circled{$i$} corresponds both to the incident and the partially transmitted radiation, \circled{1} is the reflected component and \circled{2} is the additional transmitted component.

\begin{figure}[t]
  \includegraphics{{Figures/Fig2}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 1.650$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.070$~rad/fs. (a) time-domain view (b) input and output spectra (c) resonance conditions diagram.}%
  \label{fig:Fig2}
\end{figure}

The second configuration (seen in Fig.~\ref{fig:Fig3}) is a case with significant difference between $k_{1}$ and $k_{2}$. Since~\eqref{eq:Type1ResonanceCondition} is no longer degenerate, the resonance diagram in Fig.~\ref{fig:Fig3}c is more complex. However, as one can notice, in that case only solution marked with \circled{2}, corresponding to the upper (i.e. ``$-, +$'') branch of~\eqref{eq:Type1ResonanceCondition}, contributes to the scattered radiation. Component \circled{1}, corresponding to the scattered radiation, comes from~\eqref{eq:Type0ResonanceCondition}. The unmarked spectral line close to $\omega \approx 2.4$ is the Cherenkov radiation of the soliton itself.

\begin{figure}[t]
  \includegraphics{{Figures/Fig3}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 1.500$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.150$~rad/fs. (a) time-domain view (b) input and output spectra (c) resonance conditions diagram.}%
  \label{fig:Fig3}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics{{Figures/Fig4}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 3.500$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.085$~rad/fs. (a) time-domain view (b) input and output spectra (c) resonance conditions diagram.}%
  \label{fig:Fig4}
\end{figure}

>>>>

\date{\today}

@@

Once we suppress the initial radiation that is shed by the seed soliton during the relaxation process, the isolated soliton propagates generating a narrow-spectrum Cherenkov radiation. As an example we can consider Fig.~\ref{fig:Fig1}. Panel Fig.~\ref{fig:Fig1}b shows normalized spectral densities at the input and the output of the simulation. The difference in spectra between the input and the output can be also seen in a logarithmic scale on panel Fig.~\ref{fig:Fig1}c. There one can notice that on top of the input spectrum (plotted by thin black line) arise two additional spectral lines in the output spectrum (plotted by thicker gray line). Panel Fig.~\ref{fig:Fig2}d demonstrates resonance conditions~\eqref{eq:CherenkovRadiationResonanceCondition} and~\eqref{eq:FWMRadiationResonanceCondition}: black curve corresponds to the left-hand's side of both equations $\beta(\omega)$, horizontal lines correspond to the right-hand's sides. Intersections between the dispersive curve and the horizontal lines that contribute to Cherenkov radiation are marked separately: \circled{1}~is the radiation due to the second component of the soliton as predicted by equation~\eqref{eq:CherenkovRadiationResonanceCondition}, \circled{2}~is due to beat between the components with wavenumber $2 k_{2} - k_{1}$ as predicted by~\eqref{eq:FWMRadiationResonanceCondition}.

\begin{figure}[t]
  \includegraphics{{Figures/Fig1}.pdf}
  \caption{(color online) Cherenkov radiation of an isolated soliton produced by the soliton with $\omega_{1} = 1.010$~rad/fs. (a) time-domain view, (b) input and output spectra (c) spectra difference in log scale, and (d) resonance conditions diagram.}%
  \label{fig:Fig1}
\end{figure}

@@

The first configuration we consider is very close to the degenerate case where the wavenumbers of the individual soliton components $k_{1}$ and $k_{2}$ coincide. Equation~\eqref{eq:Type1ResonanceCondition} then turns into equation~\eqref{eq:Type0ResonanceCondition}. This case resembles the case of fundamental single-component solitons~\cite{yulin2004four}. However, due to shape of the dispersive curve $\beta(\omega)$ there is now more than one nontrivial solution to equation~\eqref{eq:Type0ResonanceCondition} and a single incident frequency corresponds up to four possible resonances. This configuration can be seen in Fig.~\ref{fig:Fig1}. In practice, only some of them actually contribute to the scattered radiation. Again, those solution are separately marked on a diagram on panel~\ref{fig:Fig1}d: \circled{$i$} corresponds both to the incident and the partially transmitted radiation, \circled{1} is the reflected component and \circled{2} is the additional transmitted component.

\begin{figure}[t]
  \includegraphics{{Figures/Fig2}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 1.650$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.070$~rad/fs. (a) time-domain view, (b) input and output spectra (c) spectra difference in log scale, and (d) resonance conditions diagram.}%
  \label{fig:Fig2}
\end{figure}

The second configuration (seen in Fig.~\ref{fig:Fig3}) is a case with significant difference between $k_{1}$ and $k_{2}$. Since~\eqref{eq:Type1ResonanceCondition} is no longer degenerate, the resonance diagram in Fig.~\ref{fig:Fig3}d is more complex. However, as one can notice, in that case only solution marked with \circled{2}, corresponding to the upper (i.e. ``$-, +$'') branch of~\eqref{eq:Type1ResonanceCondition}, contributes to the scattered radiation. Component \circled{1}, corresponding to the scattered radiation, comes from~\eqref{eq:Type0ResonanceCondition}. The unmarked spectral line close to $\omega \approx 2.4$ is the Cherenkov radiation of the soliton itself.

\begin{figure}[t]
  \includegraphics{{Figures/Fig3}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 1.500$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.150$~rad/fs. (a) time-domain view, (b) input and output spectra (c) spectra difference in log scale, and (d) resonance conditions diagram.}%
  \label{fig:Fig3}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics{{Figures/Fig4}.pdf}
  \caption{(color online) Scattering of a weak DW with carrier frequency $\omega_{\text{inc}} = 3.500$~rad/fs on a soliton with first-component carrier frequency $\omega_{1} = 1.085$~rad/fs. (a) time-domain view, (b) input and output spectra (c) spectra difference in log scale, and (d) resonance conditions diagram.}%
  \label{fig:Fig4}
\end{figure}

### 2022-06-24 text/Supplementary.tex

\documentclass[a4paper,11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}

\newcommand{\abs}[1]{\left| #1 \right|}

\title{Supplementary Material}
\date{\today}

@@

@@

When analyzing the nonlinear scattering near an oscillatory mode we have used an expression for the oscillation frequency. In this section we will derive this expression.

Let us return to equation (3) for coupled solitons. We can re-normalize the equations by performing the following transformation
\begin{equation*}
  U_{n} \to \gamma_{n}^{1/2} e^{i \beta_{n} z} \cdot U_{n},
\end{equation*}
which will make the equations symmetric
\begin{equation*}
  i \partial_{z} U_{n}
    - \frac{1}{2} \beta''_{n} \partial_{t}^{2} U_{n}
    + \gamma_{n}^{2} \abs{U_{n}}^{2} U_{n}
    + 2 \gamma_{n} \gamma_{m} \abs{U_{m}}^{2} U_{n} = 0.
\end{equation*}
This in turn allows us to recognize the modified couple of equations as Euler-Lagrange equations for Lagrangian
\begin{equation*}
  \int \limits_{-\infty}^{+\infty}
    \mathcal{L}(U_{1}, \partial_{z} U_{1}, \partial_{t} U_{1}, \ldots)
    \, dt,
\end{equation*}
where Lagrangian density $\mathcal{L}$ is defined as a sum of three components $\mathcal{L} = \mathcal{L}_{1} + \mathcal{L}_{2} + \mathcal{L}_{\text{int}}$, with $L_{n}$ being a single-soliton Lagrangian density
\begin{equation}
  \label{eq:SingleSolitonLagrangianDensity}
  \mathcal{L}_{n} =
  \frac{i}{2} \left(
    \partial_{z} U_{n} \cdot U_{n}^{*} -
    \partial_{z} U_{n}^{*} \cdot U_{n}
  \right)
  + \frac{1}{2} \beta''_{n} \, \partial_{t} U_{n} \partial_{t} U_{n}^{*}
  + \frac{1}{2} \gamma_{n}^{2} \, \abs{U_{n}}^{4},
\end{equation}
and $\mathcal{L}_{\text{int}}$ being the interaction term
\begin{equation}
  \label{eq:InteractionLagrangianDensity}
  \mathcal{L}_{\text{int}} =
    2 \gamma_{1} \gamma_{2}
    \abs{U_{1}}^{2} \abs{U_{2}}^{2}.
\end{equation}
Let us assume that the soliton components $U_{n}$ can be described by the following generic \textit{ansatz}
\begin{equation}
  \label{eq:SolitonAnsatz}
  U_{n}(z, t) = A_{n}(z) S\left(
    \frac{t - t_{n}(z)}{\sigma_{n}(z)}
  \right) \exp\left(
    - i \Omega_{n}(z) t + i \phi_{n}(z)
  \right).
\end{equation}
In here $A_{n}$ is the amplitude of the pulse, $t_{n}$ is the central position, $\sigma_{n}$ is the pulse width, $\Omega_{n}$ is the frequency detuning, $\phi_{n}$ is the phase, and $S(x)$ is function that defines the envelope shape. At the moment we will not specify the concrete form of $S(x)$, but will assume that it is an even function. Substituting \eqref{eq:SolitonAnsatz} into \eqref{eq:SingleSolitonLagrangianDensity} and \eqref{eq:InteractionLagrangianDensity} and integrating over $t$ we arrive at the expressions for the averaged Lagrangians
\begin{gather}
  L_{n} =
    I_{1} \, t_{n} \sigma_{n} A_{n}^{2} \frac{d \Omega_{n}}{d z} +
    I_{1} \, \sigma_{n} A_{n}^{2} \frac{d \phi_{n}}{d z} +
    I_{2} \, \frac{\beta''_{n}}{2} \frac{A_{n}^{2}}{\sigma_{n}} \nonumber \\
    + I_{1} \, \frac{\beta''_{n}}{2} \sigma_{n} A_{n}^{2} \Omega_{n}^{2} +
    I_{3} \, \frac{\gamma_{n}^{2}}{2} \sigma_{n} A_{n}^{4} \\
  L_{\text{int}} =
    2 \, \gamma_{1} \gamma_{2} \, A_{1}^{2} A_{2}^{2} \,
    I_{\text{int}}(\sigma_{1}, \sigma_{2}, t_{1}, t_{2}),
\end{gather}
where the following integrals have been defined
\begin{align*}
  I_{1} =
    \int \limits_{-\infty}^{+\infty}
    S^{2}(x) \, dx &&
  I_{2} =
    \int \limits_{-\infty}^{+\infty}
    (S'(x))^{2} \, dx \\
  I_{3} =
    \int \limits_{-\infty}^{+\infty}
    S^{4}(x) \, dx &&
  I_{\text{int}} =
    \int \limits_{-\infty}^{+\infty}
    S^{2}\left(
      \frac{t - t_{1}}{\sigma_{1}}
    \right)
    S^{2}\left(
      \frac{t - t_{2}}{\sigma_{2}}
    \right) \, dt
\end{align*}
Due to the time invariance in the problem, $I_{\text{int}}$ depends only on the difference between $t_{1}$ and $t_{2}$
\begin{equation*}
  I_{\text{int}} = I_{\text{int}}(t_{1} - t_{2}, \sigma_{1}, \sigma_{2}),
\end{equation*}
and it is an even function of that difference.

>>>>

\documentclass[a4paper, 11pt]{article}
\pdfoutput=1

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage[utf8]{inputenc}

\newcommand{\abs}[1]{\left| #1 \right|}
\renewcommand{\theequation}{S.\arabic{equation}}

@@

\title{Supplementary Material}

\author[1]{Ivan Oreshnikov}
\author[2,3,4]{Oliver Melchert}
\author[2,3]{Stephanie Willms}
\author[3]{Surajit Bose}
\author[2,3]{Ihar Babushkin}
\author[2,3,4]{Ayhan Demircan}
\author[5]{Alexey Yulin}

\affil[1]{Max Planck Institute for Intelligent Systems, Max-Planck-Ring 4, 72076 T\"ubingen, Germany}
\affil[2]{Cluster of Exellence PhoenixD, Welfengarten 1, 30167 Hannover, Germany}
\affil[3]{Institute of Quantum Optics, Leibniz Universit\"at Hannover, Welfengarten 1, 30167 Hannover, Germany}
\affil[4]{Hannover Centre for Optical Technologies, Neinburger Strasse 17, 30167 Hannover, Germany}
\affil[5]{Department of Nanophotonics and Metamaterials, ITMO University, Kronverskiy pr. 49, 19701 St.~Petersburg, Russia}

\date{\today}

@@

When analyzing the nonlinear scattering near an oscillatory mode we used an expression for the oscillation frequency. In this section we will derive this expression.

Let us return to equation (3) for coupled solitons. We can re-normalize the equations by performing the following transformation
\begin{equation*}
  U_{n} \to \gamma_{n}^{1/2} e^{i \beta_{n} z} \cdot U_{n},
\end{equation*}
which will make the equations symmetric
\begin{equation*}
  i \partial_{z} U_{n}
    - \frac{1}{2} \beta''_{n} \partial_{t}^{2} U_{n}
    + \gamma_{n}^{2} \abs{U_{n}}^{2} U_{n}
    + 2 \gamma_{n} \gamma_{m} \abs{U_{m}}^{2} U_{n} = 0.
\end{equation*}
This in turn allows us to recognize the modified couple of equations as Euler-Lagrange equations for Lagrangian
\begin{equation*}
  \int \limits_{-\infty}^{+\infty}
    \mathcal{L}(U_{1}, \partial_{z} U_{1}, \partial_{t} U_{1}, \ldots)
    \, dt,
\end{equation*}
where Lagrangian density $\mathcal{L}$ is defined as a sum of three components $\mathcal{L} = \mathcal{L}_{1} + \mathcal{L}_{2} + \mathcal{L}_{\text{int}}$, with $L_{n}$ being a single-soliton Lagrangian density
\begin{equation}
  \label{eq:SingleSolitonLagrangianDensity}
  \mathcal{L}_{n} =
  \frac{i}{2} \left(
    \partial_{z} U_{n} \cdot U_{n}^{*} -
    \partial_{z} U_{n}^{*} \cdot U_{n}
  \right)
  + \frac{1}{2} \beta''_{n} \, \partial_{t} U_{n} \partial_{t} U_{n}^{*}
  + \frac{1}{2} \gamma_{n}^{2} \, \abs{U_{n}}^{4},
\end{equation}
and $\mathcal{L}_{\text{int}}$ being the interaction term
\begin{equation}
  \label{eq:InteractionLagrangianDensity}
  \mathcal{L}_{\text{int}} =
    2 \gamma_{1} \gamma_{2}
    \abs{U_{1}}^{2} \abs{U_{2}}^{2}.
\end{equation}
Let us assume that the soliton components $U_{n}$ can be described by the following generic \textit{ansatz}
\begin{equation}
  \label{eq:SolitonAnsatz}
  U_{n}(z, t) = A_{n}(z) S\left(
    \frac{t - t_{n}(z)}{\sigma_{n}(z)}
  \right) \exp\left(
    - i \Omega_{n}(z) t + i \phi_{n}(z)
  \right).
\end{equation}
In here $A_{n}$ is the amplitude of the pulse, $t_{n}$ is the central position, $\sigma_{n}$ is the pulse width, $\Omega_{n}$ is the frequency detuning, $\phi_{n}$ is the phase, and $S(x)$ is function that defines the envelope shape. At the moment we will not specify the concrete form of $S(x)$, but will assume that it is an even function.

Before we continue let us stress one important thing: this ansatz cannot express all the possible internal oscillations of the soliton. One obvious example, as it was noted in the text, is the case of the pulse-width oscillation. In order to capture this dynamics, we need to add frequency chirp to the ansatz.

Substituting \eqref{eq:SolitonAnsatz} into \eqref{eq:SingleSolitonLagrangianDensity} and \eqref{eq:InteractionLagrangianDensity} and integrating over $t$ we arrive at the expressions for the averaged Lagrangians
\begin{gather}
  L_{n} =
    I_{1} \, t_{n} \sigma_{n} A_{n}^{2} \frac{d \Omega_{n}}{d z} +
    I_{1} \, \sigma_{n} A_{n}^{2} \frac{d \phi_{n}}{d z} +
    I_{2} \, \frac{\beta''_{n}}{2} \frac{A_{n}^{2}}{\sigma_{n}} \nonumber \\
    + I_{1} \, \frac{\beta''_{n}}{2} \sigma_{n} A_{n}^{2} \Omega_{n}^{2} +
    I_{3} \, \frac{\gamma_{n}^{2}}{2} \sigma_{n} A_{n}^{4} \\
  L_{\text{int}} =
    2 \, \gamma_{1} \gamma_{2} \, A_{1}^{2} A_{2}^{2} \,
    I_{\text{int}}(\sigma_{1}, \sigma_{2}, t_{1}, t_{2}),
\end{gather}
where the following integrals have been defined
\begin{align*}
  I_{1} =
    \int \limits_{-\infty}^{+\infty}
    S^{2}(x) \, dx &&
  I_{2} =
    \int \limits_{-\infty}^{+\infty}
    (S'(x))^{2} \, dx \\
  I_{3} =
    \int \limits_{-\infty}^{+\infty}
    S^{4}(x) \, dx &&
  I_{\text{int}} =
    \int \limits_{-\infty}^{+\infty}
    S^{2}\left(
      \frac{t - t_{1}}{\sigma_{1}}
    \right)
    S^{2}\left(
      \frac{t - t_{2}}{\sigma_{2}}
    \right) \, dt
\end{align*}
Due to the time invariance in the problem, $I_{\text{int}}$ depends only on the difference between $t_{1}$ and $t_{2}$
\begin{equation*}
  I_{\text{int}} = I_{\text{int}}(t_{1} - t_{2}, \sigma_{1}, \sigma_{2}),
\end{equation*}
and it is an even function of that difference.
